\acknowledgments

It was wonderful! 

I admit that I truly enjoyed it. I will miss these four years with all the great conversations, all the laughs, all the stress, all the deadlines, all the happiness and sadness after conference notifications,  all the cool but never working ideas, all the not-so-great foods at the university cafeteria, all the foosball matches, all the soos talks and reading groups, all the slurm jobs, all the memory exhausted errors, all Chang's unfunny jokes, all the coffee breaks, and finally Bob.\footnote{Bob is the mammoth in the common room of third floor of Science Park 904.} But what I miss the most is the amazing group of people I met during these years.

In all these years I had the chance to \textbf{learn with perfect supervision} from Jaap and Maarten. 

When I arrived in Amsterdam, Jaap was on a sailing trip with his boat (on which he never took me!) and at some point, someone told me he got stuck in a storm and I understood that my PhD under his supervision was going to be an adventurous journey. Jaap, thanks for giving me the opportunity in the first place, helping me to grow, teaching me how to do research, and chipping in with me for all the things that I wanted to do during my PhD. 

I also wish to thank Maarten, who is an endless source of knowledge and experience (and knows a lot of old songs!). Maarten has built ILPS,  an excellent group that is a perfect platform to grow successful people. He cares for everyone in the group to have a great experience. It was an honor to be part of this group. Maarten, thanks for investing in me and for being a supportive supervisor and a fantastic mentor. 

I am also honored to have Arianna, Bruce, Claudia, Evangelos, Max, and Stephan as my committee members. Thanks for generously offering your time.

The next one to thank is Hosein, my buddy. When we got the offer to do our PhD on the same project at the University of Amsterdam, I promised to play PES (Pro Evolution Soccer) with him every single day till the end of our PhD. Four years have passed and I still haven't played with him even a single time. My sincere apologies Hosein for not fulfilling my promise, but I will eventually make it up to you.

The amazing people of ILPS and ILLC. Being part of these groups was the highlight of these four years. 

I want to thank all the senior members and staff: Christof, Debbie, Evangelos, Fennike, Hinda, Jenny, Karine, Petra, Sonja, and Tanja. It was so pleasant to work with you.
Special thanks to Maarten Marx for helping me at the beginning to get on board with my research. Maarten, thanks for all the fun and great conversations and remarkable guidance.

Also, I want to thank my fellow Master and PhD students, as well as great postdocs, for making these past years fun and exciting for me. Adith, Arezoo, Arnold, Aldo, Aleksandr, Alex, Alexey, Ali A, Ali V, Amir, Ana, Anna, Anne, Antonis, Arianna, Artem, Bob, Boris, Chang, Christophe, Chuan, Cristina, Daan, Damien, Dan, Dat, David, David, Dilek, Eva, Evgeny, Fei, Giorgos, Hamid, Harrie, Hendra, Hendrik, Hendrike, Hugo, Ilya, Isaac, Ivan, Jiahuan, Jie, Jin, Joost, Julia, Julien, Kaspar, Katya, Ke, Lars, Maartje, Mariya, Mahsa, Manos, Marc, Mariya, Marlies, Marzieh, Masrour, Maurits, Mohammad, Mozhdeh, Nikos, Olivier, Pengjie, Petra, Praveen, Richard, Ridho, Rolf, Sam, Sami, Shangsong, Shaojie, Spyretta, Svitlana, Tobias, Tom, Trond, Vera, Wanuy, Xiaohui, Xiaojuan, Xinyi, Yaser, Yangjun, Yifan, Zhaochun and Ziming, thanks for being so fantastic.  I had so many great moments with every single one of you and I wish you all unlimited success and happiness.


During my PhD, I had the chance to intern at Google and Apple. I came back with plenty of new skills and ideas and warm memories of creative people there. Aleksey, Anna, Behrang, Enrique, Jakob, Jason, Lukasz, Manish, Marvin, Oriol, Pascal, Sascha, Stephan, Zoha, and Zina, thank you so much for making my internships such a great experience for me. 

This is already getting really long, but I also want to thank my friends, colleagues, and family. They may not know how much they helped by just being in my life. Abbas, Afra, Ali, Alireza, Alexey, Amir, Amir Hossein, Amin, Arash, Arman, Aryaz, Atieh, Avital, Azadeh, Aziz, Babak, Behrooz, Casper, Danial, Dena, Elham, Erfan, Faegheh, Fahimeh, Fatemeh Zahra, Fereshteh, Hadi, Hamed, Hamid, Hamraz, Hoda, Hodjat, Hugo, Iman, Irene, Jonathan, Keyvan, Lasse, Leila, Liliana, Majid, Manoj, Maryam, Marzieh, Masoud, Masoumeh, Mehdi, Mehran, Melika, Mina, Mojdeh, Mojtaba, Mohammad, Mohammad Ali, Mohammad Hosein, Mohammad Reza, Mohammad Sadegh, Mohsen, Moslem, Nal, Nasrin, Neda, Niloofar, Noushin, Paniz, Panos, Parisa, Pegah, Pooya, Rasoul, Reza, Rianne, Rozhin, Sara, Sahar, Sanaz, Shayan, Shima, Spyretta, Thomas, Tim, Vahab, Yaser, and Zahra thank you so much. You are fantastic!

Mom, dad; this wouldn't be possible without you and your never-ending love and support. You are always my main driving motivation and I always admire you. Thanks for everything you have done for me. I wish I was able to spend more time with you during the past years, but you were in my heart every single moment.

I also want to thank the coolest siblings in the world, Mohsen and Zohre. Hanging out with you guys gave me a lot of positive energy during these years. You are the best!

Samira, however, tops the acknowledgments. Samira is the smartest and kindest person I know and having her next to me, every single day is just amazing.  During these years, she listened to all my half-baked ideas and helped me solve many hard problems and fix so many nasty bugs, but more importantly, she adapted her life and decisions to just make it easier for me so many times and that is why I owe her a really giant thank you. Thank you for being so awesome, Samira!


\hfill 

Mostafa Dehghani\\
Winter of 2020.

\afterpage{\blankpage}